---
title: "Brazilian Vegetation Analysis and Prediction"
author: "Amol Madhukar Nanaware"
date: "20/06/2020"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.


## References

- Rios, Ricardo; Nogueira, Tatiane; Palma, Gabriel; Mello, Rodrigo (2019), “Brazilian Forest Dataset”, Mendeley Data, v2 http://dx.doi.org/10.17632/9x62992sw6.2

- Philipp Graeser, Predicting plant species distributions on a local scale for conservation
planning: A comparison of different modelling techniques,  https://www.geos.ed.ac.uk/~mscgis/07-08/s0787618/

- Kiran Karkera, Regression Models with multiple target variables,  https://towardsdatascience.com/regression-models-with-multiple-target-variables-8baa75aacd


## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

